---
title: "Week 9, Day 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(PPBDS.data)
library(rstanarm)
library(tidyverse)

# There is one change to our data from Tuesday. We have a created a new
# variable: `poverty_n`, where the "n" stands for "normalized." To normalize data
# is to subtract the mean and divide by the standard deviation. This can be
# helpful. The coefficient to such a variable can be interpreted as a comparison
# between two groups, separated by a one standard deviation of the poverty
# measure.


week_9 <- kenya %>% 
  rename(reg_chg = reg_byrv13) %>% 
  filter(treatment %in% c("control", "local")) %>% 
  droplevels() %>% 
  mutate(poverty_n = (poverty - mean(poverty))/sd(poverty)) %>% 
  select(poll_station, reg_chg, treatment, poverty_n, poverty)
  
```


## Scene 1

**Prompt:** Let's create a new model. Consider `reg_chg` as a function of `treatment`, `poverty_n` and the interaction between the two.

* Write the math for this model.

$$ reg\_chg = \beta_0 + \beta_1 x_{t,i} + \beta_2 x_{p,i} + \beta_2 x_{t*p} + \epsilon_i$$

* Describe the population for which you are creating the model.

```{r}
# Our population will include all Kenyan's
```


* Fit the  model and interpret the coefficients. Focus on the coefficient of the interaction term.


```{r}
fit_obj <- stan_glm(data = week_9,
                    formula = reg_chg ~ treatment*poverty_n, 
                    family = gaussian(),
                    refresh = 0)

print(fit_obj, digits = 5)

# The median of our intercept (.00423) represents the median of our estimated posterior # The distribution for the average reg_chg (registration change) as a function of poverty_n and treatment when both of the predictors are held 0
# treatmentlocal median average between treatment and control group when poverty_n is equal to zero. 
# Poverty_n median represents the average change reg_chg when treatment local is held at 0  
```


## Scene 2

**Prompt:** Let's begin with a question from Kenyan President Uhuru Kenyatta:

*Consider the polling station 007/001. What are the chances of an increase in registration of 4% if I were to give it the local treatment in January?*

Write a sentence or two for each of these topics:

* What would Wisdom suggest about the use of the `kenya` data to answer this question?

The data data in `Kenya` dataset is related to what is being asked in the question and thus can be helpful in estimating the increase in registration in station 007/001. However, one limitation this data has is that we don't know what time period the data is coming from.

* Describe the ideal Preceptor Table.

The ideal PT would have treatment and control imposed on each polling station and predictive outcome for each individual station. There'd be a monthly observation for each month, particularly January. 


* Graph the posterior probability distribution `reg_chg` if polling station 007/001 were to be assigned treatment in January.

```{r}
new_obs <- tibble(treatment = "local", 
                  poverty_n = -1.60835093)

                 pp <- posterior_predict(fit_obj, new_obs) %>%
                   as_tibble() %>%
                   mutate(as.numeric()) %>%
                   rename(predictions = `1`)
                   ggplot(aes(x = )) +
                     geom_histogram(aes(y = after_stat(count/sum(count))))
                   
              

kenya
```


* Answer the President's question.


## Scene 3


**Prompt:**  President Kenyatta has another question:

*I care more about increasing registration in poor communities. For a community with poverty_n equal to 2, what would you expect the change in registration under treatment to be?*

Using the model which you created in Scene 1, create a graphic of the posterior probability distribution of the causal effect of `local` treatment in polling stations which have +2 sigma poverty rates. Note that there are two ways to do this. First, we can use a parameter approach. This is what we did in class last week. Second, we can use `posterior_epred()`, which is generally easier since it does the math for us. Use the `posterior_epred()` approach. 



